---
name: Barry Quinn
address: "Queen's Business School,\\tabularnewline Queen's University Belfast, BT9 1NN, N. Ireland."
www: quinference.com
phone: +44 787 238 2074
email: "b.quinn@qub.ac.uk"
twitter: con0metrix
github: quinfer
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position:  BSc (Hons), PhD, CStat
bibliography: [bqpubs.bib]
format: cv-pdf
header-includes:
  \definecolor{headcolor}{HTML}{000088}
---

\newcounter{bib}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(dplyr)
library(RefManageR)
library(gcite)
source("functions.R")

# Google scholar stats
bq <- gcite_citation_index(
  gcite_url("https://scholar.google.com/citations?user=q6wJceEAAAAJ&hl=en")
)

# Read any bib files
pubs <- ReadBib("bqpubs.bib", check = FALSE)

# Read grants file
grants <- readr::read_csv("Grant_income.csv")

```

# Education and qualifications

```{r degrees, results='asis'}
tribble(
  ~Degree, ~Institution, ~Year,
  "B.Sc.(Hons)", "Queen's University Belfast", 1995,
  "MSc","RMIT University Melbourne",2006,
  "Ph.D.", "Queen's University Belfast", 2012,
  "C.Stat.", "Royal Statistical Society", 2019
) |>
  baretable()
```

# Fellowships

  * Fellow of the Institute of Electronics, Communication and Information Technology in Queen's University Belfast (elected 2021).
  * Fellow of the Centre for Responsible Banking and Finance, Edinburgh (elected 2013).

# Employment history

```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position,
  1995, 1998, "\\textbf{Financial Adviser}, City Financial Partners, London",
  1998, 2000, "\\textbf{Unit Trust Dealer}, Janus Henderson Investors, London",
  2000, 2004, "\\textbf{Currency Trader/Liquidity Manager}, Janus Henderson Investors, London",
  2005, 2005, "\\textbf{Teaching Fellow}, Department of Finance, RMIT University Melbourne",
  2009, 2009, "\\textbf{Teaching Fellow}, Business School, Ulster University",
  2010, 2020, "\\textbf{Lecturer}, Department of Finance, Queen's Management School",
  2020, 2023, "\\textbf{Senior Lecturer},Department of Finance, Queen's Management School"
) |>
  arrange(-Start) |>
  mutate(
    Start = as.character(Start),
    End = as.character(End),
    End = tidyr::replace_na(End, ""),
    Years = if_else(End == Start,
      as.character(Start),
      paste(Start, "--", End, sep = ""),
      paste(Start, "--", End, sep = "")
    )
  ) |>
  select(Years, Position) |>
  baretable()
```

# Academic and research leadership

  * **Director**, Finance, Technology and AI lab, Queen's University Belfast. 2022--.
  * **QUB Academic Lead**, Steering group for Northern Ireland global centre in secure connected intelligence for regulatory technology in finance.
  * **Programme Director**, MSc Quantitative Finance, Queen's University Belfast. 2012--2021.
  * **Founder**, Queen's Student Managed Fund, 2012--2023.

# Awards and honours

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2016, "QUB Teaching Award"
) |>
  filter(!grepl("HP Innovation", Award)) |>
  baretable()
```


# Research

  * Since 2012 I have authored `r NROW(pubs)` papers and reports on topics in econometrics and data science, state-of-the-art efficiency and productivity analysis, risk implications of policy actions in banking and climate finance, and association football economics.
  * On Google Scholar my h-index is `r bq$All[2]` with total citations of `r prettyNum(bq$All[1], big.mark=",")` (as at `r format(Sys.time(), "%e %B %Y")`).
  * My current research involves the application of statistics and machine learning to complex problems in, capital regulation, systemic risk, climate risk and trade surveillance.
  * I currently supervise six PhD students (one visiting PhD student). I have previously supervised an additional three PhD students and ten Masters students.

# Public Teaching lectures

* PhD Seminar, *Causality and AI*, Queen's Management School, Belfast, April 2023  
* PhD Seminar, *Statistical inference for busines school research: Part 1*, Queen's Management School, Belfast, April 2022 
* PhD Seminar, *Statistical inference for busines school research: The statistics strike back*, Queen's Management School, Belfast, Aug 2022 

\enlargethispage*{0.6cm}

# Major conference presentations

* Keynote Speaker, *Estimating Systemic Risk*, Irish Finance Association, Maynooth University, Ireland, April 2023
* Invited Talk, *Teaching data science in the age of FinTech*, Royal Statistics Society Annual Conference, Aberdeen UK, Sep 2022.
* Invited Talk, *Carbon pricing and machine learning*, Multidisciplinary Workshop on Fintech, Islamic Finance and Sustainability (online), Hamad Bin Khalifa University, Qatar, Nov 2022.
* Invited Speaker, *Understanding fintech and financial stability* ,International Workshop on Financial System Architecture and Stability, Bayes Business School, London, Sept 2018
* Invited Speaker, *Systemic Risk and Basel Compliance*,British Accounting and Finance Association Annual Conference,London, April 2018.
* Invited Speaker, *Diffential regulation of Irish credit unions: Does one size fit all?*, 2nd Conference on Comtemporary Issues in Banking ,Centre for Responsible Banking and Finance, St Andrews, Dec 2017.
* Invited Speaker, *Business model diversity, efficiency and productivity of cooperatives*, European workshop in efficiency and productivity analysis, Aalto University, Finland, Jun 2017.
* Invited Panelist, *Statistical inference and credibility in finance*, Emerging Scholars in Banking and Finance, Bayes Business School, London, Dec 2016.
* Invited Speaker, *Capital regulation compliance and the performance of European banks*, International Workshop on Financial System Architecture and Stability, HEC Montreal, Aug 2016.
* Participant, *Bloomberg Annual Educational Symposium*, Bloomberg London HQ, Sep 2015.
  

# Research income

```{r grants}
sumgrants <- grants |>
  pull(Amount) |>
  sum(na.rm = TRUE)
```

I have acquired (in most cases jointly) £`r sumgrants/1e6` million in external research grants since 2010. External research grants over £70,000 are listed below.\vspace*{0.2cm}\enlargethispage*{0.5cm}

```{r grantstable, results='asis'}
grants |>
  filter(Amount > 69999, Type == "Research") |>
  mutate(
    Time = paste0(Start, ifelse(is.na(End), "", paste0("--", End))),
    Entry = paste(People, ". ``", Title, "''. ",
      "\\emph{Funding from ", Source, "}",
      sep = ""
    ),
    Amount = dollars(Amount)
  ) |>
  arrange(Time, desc(Amount)) |>
  select(Time, Entry, Amount) %>%
  baretable(
    align = "llp{13.3cm}r",
    hline.after = c(0, NROW(.)),
    size = "\\fontsize{10}{15}",
    add.to.row = list(
      pos = as.list(seq(NROW(.))),
      command = rep("\\\\[-0.3cm]", NROW(.))
    )
  )
```

# Teaching
  * I design and teaching advanced topics in statistics and machine learning for finance students.
  * In the past I have taught courses in
    * Statistics for Business
    * Financial Econometrics and Data Science
    * Financial Institutions and Market
    * Trading Principles
  * I currently teach graduate level courses in AI and trading, and Advanced Financial Analytics.
  * I have also designed and delivered executive education courses in:
    * Statistical forecasting for energy markets (3-Day course for PNG Ltd demand forecasting professionals)
    * Capital Markets and Regulation (3-Day course on Axiom Ltd)
  * In every year since 2012, student evaluations for my teaching have given an average rating for my teaching above 4.5 out of 5.

# Consulting

  * Since 2016, I have worked with several different private companies in Northern Ireland. I have produced `r nrow(grants %>% filter(Type=="Consulting"))` written consulting reports listed below.
  

```{r white-papers}
#| output: asis
# Normal articles excluding editorials
pubs[bibtype = "Techreport"] |>
  add_bib_section()
```


# Refereed research papers

```{r research-papers}
#| output: asis
# Normal articles excluding editorials
pubs[bibtype = "Article"] |>
  add_bib_section()
```

# Papers in refereed conference proceedings

```{r papers-in-proceedings}
#| output: asis
pubs[bibtype = "InProceedings"] |>
  add_bib_section()
```

# Unpublished working papers

```{r working-papers}
#| output: asis
pubs[bibtype = "Unpublished"] |> 
  add_bib_section()
```


# Software (R packages)

```{r r-packages-list}
#| output: asis
# Keep order of R packages as they are already sorted by package name
pubs[bibtype = "Software"] |> 
  add_bib_section()
```

