---
name: Barry Quinn
address: "Queen's Business School,\\tabularnewline Queen's University Belfast, BT9 1NN, N. Ireland."
www: quinference.com
phone: +44 787 238 2074
email: "b.quinn@qub.ac.uk"
twitter: con0metrix
github: quinfer
date: "`r format(Sys.Date(), '%B %Y')`"
date-format: "MMMM YYYY"
position: BSc (Hons), PhD, CStat
bibliography: [bqpubs.bib]
format: cv-pdf
header-includes:
  \definecolor{headcolor}{HTML}{000088}
---

\newcounter{bib}

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(dplyr)
library(RefManageR)
library(gcite)
source("functions.R")

# Google scholar stats
bq <- gcite_citation_index(
  gcite_url("https://scholar.google.com/citations?user=q6wJceEAAAAJ&hl=en")
)

# Read any bib files
pubs <- ReadBib("bqpubs.bib", check = FALSE)

# Read grants file
grants <- readr::read_csv("Grant_income.csv")

```

# Personal Statement

As a Senior Lecturer in Finance, Technology, and Data Science at Queen's University Belfast, I bridge the gap between academic research and industry innovation. My work focuses on applying advanced statistical and machine learning techniques to complex problems in finance, with a particular emphasis on regulatory technology, systemic risk, and ethical AI development in financial services.

# Education and qualifications

```{r degrees, results='asis'}
tribble(
  ~Degree, ~Institution, ~Year,
  "B.Sc.(Hons) Accounting and Finance", "Queen's University Belfast", "1995",
  "MSc Quant Finance","RMIT University Melbourne","2006",
  "Ph.D. Finance", "Queen's University Belfast", "2012",
  "Chartered Statistician", "Royal Statistical Society", "2019",
  "MSc Artificial Intelligence","Queen's University Belfast","Graduating 2025"
) |>
  baretable()
```

# Professional Qualifications

* Chartered Statistician (CStat), Royal Statistical Society, 2019

# Employment history

```{r employment, results='asis'}
# Employment history
tribble(
  ~Start, ~End, ~Position,
  1995, "1998", "\\textbf{Financial Adviser}, City Financial Partners, London",
  1998, "2000", "\\textbf{Unit and Investment Trust Dealer}, Janus Henderson Investors, London",
  2000, "2004", "\\textbf{Currency Trader/Liquidity Manager}, Janus Henderson Investors, London",
  2005, "2005", "\\textbf{Teaching Fellow}, Department of Finance, RMIT University Melbourne",
  2009, "2009", "\\textbf{Teaching Fellow}, Business School, Ulster University",
  2010, "2020", "\\textbf{Lecturer}, Department of Finance, Queen's Management School",
  2020, "2023", "\\textbf{Senior Lecturer}, Department of Finance, Queen's Management School",
  2023, "present", "\\textbf{Senior Lecturer in Finance, Technology and Data Science}, Queen's Management School"
) |>
  arrange(desc(Start)) |>
  mutate(
    Start = as.character(Start),
    Years = if_else(End == "present",
      paste(Start, "--", End),
      paste(Start, "--", End)
    )
  ) |>
  select(Years, Position) |>
  baretable()
```

# Academic and research leadership

  * **Co-director**, Finance, Technology and AI lab, Queen's University Belfast, 2022--.
  * **QUB Academic Lead**, Steering group for Northern Ireland global centre in secure connected intelligence for regulatory technology in finance.
  * **Programme Director**, MSc Quantitative Finance, Queen's University Belfast, 2018--2022.
  * **Programme Director**, MSc Computational Finance & Trading, Queen's University Belfast, 2014--2018.
  * **Founder**, Queen's Student Managed Fund, 2012--2023.

# Awards and honours

```{r awards, results='asis'}
tribble(
  ~Year, ~Award,
  2016, "QUB Teaching Award",
  2018, "European CFA Quant Award (1st)",
  2021, "Associate Research Fellow, Global Innovation Institute"
) |>
  baretable()
```

# Skills and Expertise

* Advanced statistical modeling and machine learning
* AI applications in finance and trading
* Regulatory technology (RegTech) and compliance
* Financial risk management and systemic risk analysis
* Data science and big data analytics in finance
* Interdisciplinary research leadership

# Research

  * Since 2012, I have authored `r NROW(pubs)` papers and reports on topics in econometrics and data science, state-of-the-art efficiency and productivity analysis, risk implications of policy actions in banking and climate finance, and association football economics.
  * On Google Scholar, my h-index is `r bq$All[2]` with total citations of `r prettyNum(bq$All[1], big.mark=",")` (as of `r format(Sys.time(), "%e %B %Y")`).
  * My current research involves the application of statistics and machine learning to complex problems in finance.
  * I have extensive experience in PhD supervision:
    * Successfully supervised four PhD students to completion as principal supervisor.
    * Currently serving as principal supervisor for three PhD students.
    * Co-supervising two additional PhD students.
  * My PhD students' research spans diverse topics including firm value and gender diverse, climate risk premium and measurement uncertainty, machine learning in asset pricing, ESG metrics and XAI, and fintech applications for regulatory compliance.

# PhD Supervision

I have a strong track record in guiding doctoral research:

* **Completed Supervisions:** Successfully supervised three PhD students to completion as principal supervisor.
* **Current Supervisions:**
  * Principal supervisor for three ongoing PhD projects.
  * Co-supervisor for two additional PhD students.
* **Research Areas:** My PhD students' work covers a wide range of cutting-edge topics in finance and data science, including:
  * Climate risk modeling and financial implications
  * Machine learning applications in asset pricing
  * ESG metrics and Explainable AI (XAI)
  * Fintech innovations for financial regulation
  * Economic costs of cultural displays

This extensive supervision experience demonstrates my commitment to nurturing the next generation of researchers and my ability to guide complex, interdisciplinary projects at the intersection of finance, technology, and data science.

# Current Projects

* AI system for regulatory compliance in global investment management (2024-present)
  - Principal Investigator
  - Funded by UKFin+ (UKRI)
  - Developing AI models with enhanced reasoning capabilities for regulatory content generation
* Detecting trading anomalies using AI and machine learning (2021-2024)
  - Finance expert collaborator
  - In partnership with Citigroup's Belfast-based Market Intelligence and Data Science team

# Industry Collaboration

* FCA Mentor for Tech Sprint on market manipulation (2023-present)
* Lead academic on knowledge transfer projects with Fund Axis Ltd and Research Affiliates Inc (2022-present)
* Collaboration with Citigroup on AI applications for detecting trading anomalies (2021-2024)

# Organized Conferences and Symposia

* Symposium on AI and the Future of Financial Regulation, Queen's University Belfast, November 2023
* Chair, Panel debate on "Digital Regulation: Shaping digital markets and safeguarding consumer rights in Northern Ireland", Northern Ireland Competition Forum, May 2024

# Public Teaching lectures

* PhD Seminar, *Causality and AI*, Queen's Management School, Belfast, April 2023  
* PhD Seminar, *Statistical inference for business school research: Part 1*, Queen's Management School, Belfast, April 2022 
* PhD Seminar, *Statistical inference for business school research: The statistics strike back*, Queen's Management School, Belfast, Aug 2022 

# Major conference presentations

* Keynote Speaker, *Estimating Systemic Risk*, Irish Finance Association, Maynooth University, Ireland, April 2023
* Invited Talk, *Teaching data science in the age of FinTech*, Royal Statistics Society Annual Conference, Aberdeen UK, Sep 2022
* Invited Talk, *Carbon pricing and machine learning*, Multidisciplinary Workshop on Fintech, Islamic Finance and Sustainability (online), Hamad Bin Khalifa University, Qatar, Nov 2022
* Invited Speaker, *Understanding fintech and financial stability*, International Workshop on Financial System Architecture and Stability, Bayes Business School, London, Sept 2018
* Invited Speaker, *Systemic Risk and Basel Compliance*, British Accounting and Finance Association Annual Conference, London, April 2018
* Invited Speaker, *Differential regulation of Irish credit unions: Does one size fit all?*, 2nd Conference on Contemporary Issues in Banking, Centre for Responsible Banking and Finance, St Andrews, Dec 2017
* Invited Speaker, *Business model diversity, efficiency and productivity of cooperatives*, European workshop in efficiency and productivity analysis, Aalto University, Finland, Jun 2017
* Invited Panelist, *Statistical inference and credibility in finance*, Emerging Scholars in Banking and Finance, Bayes Business School, London, Dec 2016
* Invited Speaker, *Capital regulation compliance and the performance of European banks*, International Workshop on Financial System Architecture and Stability, HEC Montreal, Aug 2016
* Participant, *Bloomberg Annual Educational Symposium*, Bloomberg London HQ, Sep 2015

# Research income

```{r grants}
sumgrants <- grants |>
  pull(Amount) |>
  sum(na.rm = TRUE)
```

I have acquired (in most cases jointly) £`r sumgrants/1e6` million in external research grants since 2010. External research grants over £70,000 are listed below.\vspace*{0.2cm}\enlargethispage*{0.5cm}

```{r grantstable, results='asis'}
grants |>
  filter(Amount > 69999, Type == "Research") |>
  mutate(
    Time = paste0(Start, ifelse(is.na(End), "", paste0("--", End))),
    Entry = paste(People, ". ``", Title, "''. ",
      "\\emph{Funding from ", Source, "}",
      sep = ""
    ),
    Amount = dollars(Amount)
  ) |>
  arrange(Time, desc(Amount)) |>
  select(Time, Entry, Amount) %>%
  baretable(
    align = "llp{13.3cm}r",
    hline.after = c(0, NROW(.)),
    size = "\\fontsize{10}{15}",
    add.to.row = list(
      pos = as.list(seq(NROW(.))),
      command = rep("\\\\[-0.3cm]", NROW(.))
    )
  )
```

# Teaching

  * I design and teach advanced topics in statistics and machine learning for finance students.
  * I have developed and lead the PG-Cert in Financial Technology and Machine Learning in partnership with the School of Electronics, Electrical Engineering and Computer Science.
  * In the past I have taught courses in:
    * Statistics for Business
    * Financial Econometrics and Data Science
    * Financial Institutions and Markets
    * Trading Principles
  * I currently teach graduate-level courses in AI and Trading, and Advanced Financial Analytics.
  * I have also designed and delivered executive education courses in:
    * Statistical forecasting for energy markets (3-Day course for PNG Ltd demand forecasting professionals)
    * Capital Markets and Regulation (3-Day course for Axiom Ltd)
  * In every year since 2012, student evaluations for my teaching have given an average rating above 4.5 out of 5.

# Impact and Outreach

* My research on AI applications in financial regulation has informed policy discussions at the Financial Conduct Authority (FCA).
* The Finance, Technology and AI lab has become a hub for industry-academia collaboration in Northern Ireland, fostering innovation in financial technology.
* My work on ESG authentication and regulatory compliance has contributed to the development of more robust and ethical financial practices in the industry.

# Professional Memberships

* Royal Statistical Society
* [Any other relevant professional memberships]

# Consulting

  * Since 2016, I have worked with several different private companies in Northern Ireland. I have produced `r nrow(grants %>% filter(Type=="Consulting"))` written consulting reports listed below.
  
```{r white-papers}
#| output: asis
# Normal articles excluding editorials
pubs[bibtype = "Techreport"] |>
  add_bib_section()
```

# Refereed research papers

```{r research-papers}
#| output: asis
# Normal articles excluding editorials
pubs[bibtype = "Article"] |>
  add_bib_section()
```

# Papers in refereed conference proceedings

```{r papers-in-proceedings}
#| output: asis
pubs[bibtype = "InProceedings"] |>
  add_bib_section()
```

# Unpublished working papers

```{r working-papers}
#| output: asis
pubs[bibtype = "Unpublished"] |> 
  add_bib_section()
```

# Software (R packages)

```{r r-packages-list}
#| output: asis
# Keep order of R packages as they are already sorted by package name
pubs[bibtype = "Software"] |> 
  add_bib_section()
```

